What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-15 android-stacks.tex
Updated first part of exception types / IV.Bo
Replace all ' ~' by just '~' (the intent of the ~ is to put
together different words).

Made all columns with numbers right aligned in tabulars.

In recent years, we have witnessed an astonishing increase in the number of
mobile applications. These applications extend phones capabilities 
far beyond basic calls and textual messages. Such applications, however,
have to face an increasing number of threats to application robustness
 arising from failures in the underlying middleware and hardware (e.g., camera, sensors);
failures in third party services and libraries; compatibility issues~\cite{McDon13}; 
 memory and battery restrictions; and noisy external resources ~\cite{Zhang12} 
(e.g., wireless connections,GPS, bluetooth).

@@

In Java, when an application fails due to an uncaught exception, 
it automatically terminates, while the system prints a stack trace to the console, 
or on a log file ~\cite{gosling2000java}.  A typical Java stack trace consists of  the fully qualified name 
of the thrown exception and the ordered list of methods that were active on the call stack before 
the exception occurred ~\cite{gosling2000java,bloch2008effective}.

@@

 The high prevalence of NullPointerExceptions is in line with findings of earlier research~\cite{kim2013predicting,fraser20131600,csallner2004jcrasher}, as are the undocumented runtime 
exceptions signaled by the Android Platform ~\cite{kechagia2014}. 
Some of the findings of our
 study emphasize the impact of these bug hazards on the application robustness 
by mining a different source of information as the ones used in previous works. The present work 
mined issues created by developers on GitHub and Google Code, while  previous research analyzed crash reports and automated test reports.
 Furthermore, our work points to bug hazards that were not detected by previous research (i.e., cross-type wrappings, undocumented checked exceptions and undocumented runtime exceptions thrown by third-party libraries) which represent new threats to application robustness.

@@

User-defined exceptions can be either checked
 or unchecked, by extending either Exception or RuntimeException. There is a long-lasting debate 
about the pros and cons of both approaches~\cite{javatut,stackoverlow,debate}
%\footnote{152 questions in Stackoverflow are related to this debate}. 
Section ~\ref{sec:best} presents
a set of best practices related to each of them.

@@

\emph{\textbf{Exception Propagation.}} In Java, once an exception is thrown, 
the runtime environment looks for the nearest enclosing exception handler
(Java's try-catch block), and unwinds the execution stack if necessary.
This search for the handler on the invocation stack aims at increasing software reusability, 
since the invoker of an operation can handle the exception in a wider context ~\cite{miller1997issues}.

@@

\begin{table*}
  \centering
  \begin{tabular}{rcccccccc}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects}} &  \multicolumn{2}{c}{\bfseries{Occurrences}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline

@@

\emph{\textbf{Identifying the Concerns Related to Root Exceptions.}} To get a broader view of the root exceptions of stack traces,
we performed a manual inspection in order to identify the underlying
concerns related to the most frequently reported root exceptions.
Besides the exceptions related to programming mistakes mentioned before, we also looked for exceptions related to some concerns that are known as sources of faults in mobile development: concurrency ~\cite{ama2012} backward compatibility ~\cite{McDon13}, security ~\cite{enck2011study,was2010} and resource management (IO, Memory, Batery) ~\cite{Zhang12}.

@@

To perform this concern analysis, we selected a subset of all reported
root exception, consisting of 100 exceptions
reported on 95\% of all stack traces analyzed in this study. Hence, based on the inspection of the 
Javadoc related to each exception and the Java specification, we
identified the underlying concern releated to each root exception. 
Table~\ref{tab:tophundrend} contains the results of this analysis. This table also illustrates the exceptions 
that could not be directly mapped to one of the aforementioned concerns, either because they were too general (i.e., java.lang.Exception,
java.lang.RuntimeException, java.lang.Error) or because they were
related to other concerns (e.g., specific to an application or a given library).

@@

As mentioned before, using the ExceptionMiner tool in combination with manual inspections we could identify
the root exception types (i.e., RuntimeException, Error, checked Exception) as well as its origins - which were 
identified based on the package names of the signalers related to it on the stack traces (Section~\ref{sec:exceptionminer}).
Table~\ref{tab:typeroottab} presents the types and origins of root exceptions of all analyzed stack traces.

We can observe that most of the reported exceptions were runtime 
(64.85\%); and most of them were signaled by methods defined either on the Application (47.3\%)
or on the Android platform (34.3\%). We could also find runtime exceptions thrown by library code (17.7\%).

We can also see, from Table ~\ref{tab:typeroottab}, that contrasting with the other origins, most of the 
 exceptions signaled on Android Libcore (i.e., the set of libraries reused by the Android) were 
checked exceptions. Such set comprises: org.apache.harmony, org.w3c.dom, sun.misc, 
org.apache.http, org.json, org.xml, javax. Signaling checked exceptions is considered a 
good practice (see best practice IV in Section~\ref{sec:best}) because by using 
checked exceptions a library can define a precise 
\emph{exception interface} ~\cite{miller1997issues} to its clients.
 Since such libraries are heavily used  in several projects, such finding can be related to the libraries maturity.

@@

\begin{table}
\centering
\begin{tabular}{lccccrr}
    \hline
    \bfseries{Root Type} & \bfseries{Android} & \bfseries{Libcore} & \bfseries{App} & \bfseries{Lib}  & \bfseries{All} & \bfseries{\%} \\
    \hline

Runtime	&	1335	&	73	&	1843	&	690  &	3894 & 64.85\% \\  %2466+854
Error	       &	 188              &	 46	&	302             &	167	           &	691 & 11.51\%	\\
Checked	&	276           &	314	&	313          &	567	           &	1358 & 22.61\%	\\
Throwable	&	0	       &	0	&	2            &	0         &	2 & 0.03\%	\\
Undefined	&	4	&	0	&	18		&	38	   &	60	& 1.00\% \\
 \hline
All		& 1  803	&	433	&	2478	&	1462	&	6005 	\\
    \hline
  \end{tabular}
\caption{Types of root exceptions.}
  \label{tab:typeroottab}
\end{table}

\emph{\textbf{Inspecting Exception Interfaces.}}  According to the best practices mentioned before, 
 \emph{explicitly thrown} runtime exceptions 
should be documented as part of the \emph{exception interface} of libraries/framework reusable
methods. To investigate the obedience to such practice, we firstly filtered out all the exceptions implicitly
 signaled by  runtime environment (due to programming mistakes) - since these exceptions 
should not be documented on the method signature.  Then we inspected the code each method 
(defined either on Android  Aplication Framework or on third-party libraries) 
explicitly signaling a runtime exception.

@@

This result is aligned with the results of other two studies ~\cite{sacramento2006unchecked,kechagia2014}. 
One conducted by  Sacramento et al ~\cite{sacramento2006unchecked} - which observed that the
runtime exceptions in .Net programs are most often not documented. And other conducted by 
Kechagia and Spinellis ~\cite{kechagia2014} which discovered a set of methods 
on the Android API which do not documented runtime exceptions. One limitation 
of the work of Kechagia and Spinellis is that it did not filter out exceptions that,  
although runtime, should not be documented because they were implicitly signaled by the 
JVM due to resource restrictions or violations on Java semantic constraints.

@@

\emph{\textbf{On the null pointer problem.}}
The null references was firstly introduced by Tony Hoare in ALGOL W, which after some years he called his ``one-billion-dollar mistake"~\cite{hoare2}.
In this sudy, the null references were, infact, responsible for several reported issues - providing more evidences to Hoare's speech.
This observation emphasizes the importance of solutions to avoid NullPointerExceptions, such as:
(i) lightweight intra-method null pointer analysis supported by Java8 @Nullable annotations~\footnote{They are used by tools e.g., Eclipse, IntelliJ, Android Studio 0.5.5 (release Apr. 2014) to detect potential 
null pointer dereferences at compile time.};
(ii) inter-method null pointer analysis tools such as the one proposed by Nanda and Sinha ~\cite{nanda2009accurate};
or (iii) language designs which avoid null pointers, such 
as Monads ~\cite{Walde95} (i.e., used in functional languages for values that may not be available 
or computations that may fail) could improve the robustness of Java programs.

\emph{\textbf{On the need of rescues to the almost infeasible task of preventing uncaught exceptions}}
In this study we could observe undocumented runtime exceptions thrown by third party code,
and even undocumented checked exception thrown by a JNI interface.
Such undocumented exceptions make difficult, and most of the times infeasible
for the client code to protect against `unforeseen" situations that may happen 
while calling a library code. One may think that the solution for the uncaught exceptions may be to define a general handler, 
which is responsible for handling any exception that is not
adequately handled inside the applications. Although this 
solution may prevent  the system of abruptly crashing,
 such general handler will not have enough
contextual information to adequately handle the exception, 
a possible handler task is: to present a message to the user
 and restart the application. However, such handler cannot replace a carefully designed exception 
handling policy ~\cite{Robil00}, which can hardly be designed in the absence of 
third-party documentation on the exceptions that
may the thrown by it. On the other hand, documenting runtime exceptions is a tedious and error prone task, to help developers
mitigate this problem tools should be developed to automate the documentation of runtime exceptions
scraping from library code, few solutions in this directions have been proposed so far ~\cite{van2005combining}.

@@

%\noindent
\emph{Internal Validity.} We used a heuristics-based parser to mine
exceptions from issues.  Our parsing strategy was conservative by default; for
example, we only considered exception names using a fully qualified class name
as valid exception identifiers, while, in many cases, developers use the
exception name in issue description. Conservative parsing may minimize false
positives, which was our initial target, but also tends to increase false
negatives, which means that some cases may have not been identified as
exceptions or stack traces. Our limited manual inspection did not reveal such
cases. Moreover, in this study we manually mapped the concerns related to exceptions.
 To ensure the quality of the analysis, we calculated the interrater agreement after three independent 
developers classified a randomly selected sample (of 25 exception 
types from the total of 100); the interater agreement was high (96\%). 
Another threat relates to the fact that parts of our analysis 
are based on the availability of stack traces on issues reported on Github and Googlecode projects. 
In using these datasets, we make an underlying assumption: the stack traces reported on issues are 
representative of valid crash information of the applications. 
One way to mitigate such threat would be to access to the full 
set of crash data per application. Although some services exist 
to collect crash data from mobile applications ~\cite{BugSe14,BugSn14,Googl14,Acra14},
they do not provide open access to the crash reports of their client applications.
In our study, we mitigated this threat by manually inspecting
the source code associated to a subset of the reported exception stack traces.
Such subset comprises the stack traces related to the main findings 
of the study (e.g., ``undocumented runtime and checked exceptions",
and cross-type wrappings").
%\noindent

\emph{External Validity.} Our work uses GHTorrent dataset; although 
comprehensive and extensive is not an exact replica of Github. 
However, the result of this study does not depent on the analysis of
a complete Github dataset. Instead, the goal of our study was to 
pinpoint \emph{bug hazards} on the exception-related code based on 
exception stack trace mining of a subset of projects.
We limited our analysis to a subset of existing open-source Android projects.
We are aware that the exception stack traces reported 
for commercial apps can be different from the ones found in this study, and that
this subset is a small percentage of existing apps.
Such threats are similar to the ones imposed to other empirical studies 
which also used free or open-source Android apps ~\cite{Linar13,McDon13,Ruiz12}.
Moreover, several exception stack traces that support the findings of this study
refered to exceptions coming from methods defined on Android Application Framework
and third-party libraries.  Additionaly,  the \emph{bug hazards} observed in this study are due to
characteristics of Java exception model, which can impose challenges 
the robustness of not only to Android apps but also to other systems
 based on the same exception model.

@@

\textit{Empirical Studies on Exception Handling Defects.} 
Cabral and Marques~\cite{cabral2007exception} analyzed the
source code of 32 open-source systems, both for Java and .NET. They
observed that the actions inside handlers were very simple (e.g., logging and present a
message to the user). Coelho et al.  ~\cite{coelho2008assessing} performed an 
empirical study considering the fault-proneness of aspect-oriented implementations 
for handling exceptions. Two releases of both Java and AspectJ implementations were 
assessed as part of that study. Based on the use of an exception
flow analysis tool, the study revealed that the AOP  refactoring increased the 
number of uncaught exceptions, degrading the robustness of the AO version of every analyzed system.
The main limitation of approaches based static analysis based approaches are the number of false
positives they can generate, and the problems the faced when dealing with reflection libraries 
and dynamic class loading. Pingyu and Elbaum~\cite{Zhang12} were the first to perform
an empirical investigation of issues, related to exception-related bugs, on Android projects.  
They perform a small scale study on which they manually inspected the issues of 
5 Android applications. They observed that 29\% had to do with poor
exceptional handling code, this empirical study was used to motivate the development of a tool
aiming at amplifying existing tests to validate exception 
handling code associated with external resources. This work inspired ours,
 which automaticaly mined the exception stack traces embedded on issues 
reported on 639 open source Android projects. The goal of our study was
to identify common \emph{bug hazards} on the exception related code that can lead to 
failures such as uncaught exceptions.

>>>>

In recent years, we have witnessed an astonishing increase in the number of
mobile applications. These applications extend phones capabilities 
far beyond basic calls and textual messages. Such applications, however,
have to face an increasing number of threats to application robustness
 arising from failures in the underlying middleware and hardware (e.g., camera, sensors);
failures in third party services and libraries; compatibility issues~\cite{McDon13}; 
 memory and battery restrictions; and noisy external resources~\cite{Zhang12} 
(e.g., wireless connections,GPS, bluetooth).

@@

In Java, when an application fails due to an uncaught exception, 
it automatically terminates, while the system prints a stack trace to the console, 
or on a log file~\cite{gosling2000java}.  A typical Java stack trace consists of  the fully qualified name 
of the thrown exception and the ordered list of methods that were active on the call stack before 
the exception occurred~\cite{gosling2000java,bloch2008effective}.

@@

 The high prevalence of NullPointerExceptions is in line with findings of earlier research~\cite{kim2013predicting,fraser20131600,csallner2004jcrasher}, as are the undocumented runtime 
exceptions signaled by the Android Platform~\cite{kechagia2014}. 
Some of the findings of our
 study emphasize the impact of these bug hazards on the application robustness 
by mining a different source of information as the ones used in previous works. The present work 
mined issues created by developers on GitHub and Google Code, while  previous research analyzed crash reports and automated test reports.
 Furthermore, our work points to bug hazards that were not detected by previous research (i.e., cross-type wrappings, undocumented checked exceptions and undocumented runtime exceptions thrown by third-party libraries) which represent new threats to application robustness.

@@

User-defined exceptions can be either checked
 or unchecked, by extending either Exception or RuntimeException. There is a long-lasting debate 
about the pros and cons of both approaches~\cite{javatut,stackoverlow,debate}
%\footnote{152 questions in Stackoverflow are related to this debate}. 
Section~\ref{sec:best} presents
a set of best practices related to each of them.

@@

\emph{\textbf{Exception Propagation.}} In Java, once an exception is thrown, 
the runtime environment looks for the nearest enclosing exception handler
(Java's try-catch block), and unwinds the execution stack if necessary.
This search for the handler on the invocation stack aims at increasing software reusability, 
since the invoker of an operation can handle the exception in a wider context~\cite{miller1997issues}.

@@

\begin{table*}
  \centering
%  \begin{tabular}{rcccccccc}
  \begin{tabular}{lrrrrrrrr}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects}} &  \multicolumn{2}{c}{\bfseries{Occurrences}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline

@@

\emph{\textbf{Identifying the Concerns Related to Root Exceptions.}} To get a broader view of the root exceptions of stack traces,
we performed a manual inspection in order to identify the underlying
concerns related to the most frequently reported root exceptions.
Besides the exceptions related to programming mistakes mentioned before, we also looked for exceptions related to some concerns that are known as sources of faults in mobile development: concurrency~\cite{ama2012} backward compatibility~\cite{McDon13}, security~\cite{enck2011study,was2010} and resource management (IO, Memory, Batery)~\cite{Zhang12}.

@@

To perform this concern analysis, we selected a subset of all reported
root exceptions, consisting of 100 exceptions
reported in 95\% of all stack traces analyzed in this study. Hence, based on the inspection of the 
Javadoc related to each exception and the Java specification, we
identified the underlying concern releated to each root exception. 
Table~\ref{tab:tophundrend} contains the results of this analysis. This table also illustrates the exceptions 
that could not be directly mapped to one of the aforementioned concerns, either because they were too general (i.e., java.lang.Exception,
java.lang.RuntimeException, java.lang.Error) or because they were
related to other concerns (e.g., specific to an application or a given library).

@@

As mentioned before, using the ExceptionMiner tool in combination with manual inspections we could identify
the root exception \emph{type} (i.e., RuntimeException, Error, checked Exception) as well as its \emph{origin} - which we 
identified based on the package names of the signalers related to it in the stack traces (Section~\ref{sec:exceptionminer}).
Table~\ref{tab:typeroottab} presents the types and origins of root exceptions of all analyzed stack traces.

We can observe that most of the reported exceptions are of type runtime 
(64.85\%); and that the most common origins are methods defined either on the Application (47.3\%)
or on the Android platform (34.3\%). We could also find runtime exceptions thrown by library code (17.7\%).

We can also see, from Table~\ref{tab:typeroottab}, that in contrast with the other origins, most of the 
 exceptions signaled on Android Libcore (i.e., the set of libraries reused by Android) are 
checked exceptions. This set comprises: org.apache.harmony, org.w3c.dom, sun.misc, 
org.apache.http, org.json, org.xml, and javax. Signaling checked exceptions is considered a 
good practice (see best practice IV in Section~\ref{sec:best}) because by using 
checked exceptions a library can define a precise 
\emph{exception interface}~\cite{miller1997issues} to its clients.
 Since such libraries are widely used  in several projects, this
 finding can be attributed to the libraries' maturity.

@@

\begin{table}
\centering
\begin{tabular}{lrrrrrr}
    \hline
    \bfseries{Root Type} & \bfseries{Android} & \bfseries{Libcore} & \bfseries{App} & \bfseries{Lib}  & \bfseries{All} & \bfseries{\%} \\
    \hline

Runtime	&	1335	&	73	&	1843	&	690  &	3894 & 64.85\% \\  %2466+854
Error	       &	 188              &	 46	&	302             &	167	           &	691 & 11.51\%	\\
Checked	&	276           &	314	&	313          &	567	           &	1358 & 22.61\%	\\
Throwable	&	0	       &	0	&	2            &	0         &	2 & 0.03\%	\\
Undefined	&	4	&	0	&	18		&	38	   &	60	& 1.00\% \\
 \hline
All		& 1  803	&	433	&	2478	&	1462	&	6005 	\\
    \hline
  \end{tabular}
\caption{Types and origins of root exceptions.}
  \label{tab:typeroottab}
\end{table}

\emph{\textbf{Inspecting Exception Interfaces.}}  According to the best practices mentioned before, 
 \emph{explicitly thrown} runtime exceptions 
should be documented as part of the \emph{exception interface} of libraries/framework reusable
methods. To investigate the conformance to this practice, we firstly filtered out all the exceptions implicitly
 signaled by  the runtime environment (due to programming mistakes) - since these exceptions 
should not be documented on the method signature.  Then we inspected
the code for each method 
(defined either on Android  Aplication Framework or on third-party libraries) 
explicitly signaling a runtime exception.

@@

This result is aligned with the results of other two studies~\cite{sacramento2006unchecked,kechagia2014}. 
One conducted by  Sacramento et al~\cite{sacramento2006unchecked} - which observed that the
runtime exceptions in .Net programs are most often not documented. And other conducted by 
Kechagia and Spinellis~\cite{kechagia2014} which discovered a set of methods 
on the Android API which do not documented runtime exceptions. One limitation 
of the work of Kechagia and Spinellis is that it did not filter out exceptions that,  
although runtime, should not be documented because they were implicitly signaled by the 
JVM due to resource restrictions or violations on Java semantic constraints.

@@

\emph{\textbf{On the null pointer problem.}}
The null references was firstly introduced by Tony Hoare in ALGOL W, which after some years he called his ``one-billion-dollar mistake"~\cite{hoare2}.
In this sudy, the null references were, infact, responsible for several reported issues - providing more evidences to Hoare's speech.
This observation emphasizes the importance of solutions to avoid NullPointerExceptions, such as:
(i) lightweight intra-method null pointer analysis supported by Java8 @Nullable annotations~\footnote{They are used by tools e.g., Eclipse, IntelliJ, Android Studio 0.5.5 (release Apr. 2014) to detect potential 
null pointer dereferences at compile time.};
(ii) inter-method null pointer analysis tools such as the one proposed by Nanda and Sinha~\cite{nanda2009accurate};
or (iii) language designs which avoid null pointers, such 
as Monads~\cite{Walde95} (i.e., used in functional languages for values that may not be available 
or computations that may fail) could improve the robustness of Java programs.

\emph{\textbf{On the need of rescues to the almost infeasible task of preventing uncaught exceptions}}
In this study we could observe undocumented runtime exceptions thrown by third party code,
and even undocumented checked exception thrown by a JNI interface.
Such undocumented exceptions make difficult, and most of the times infeasible
for the client code to protect against `unforeseen" situations that may happen 
while calling a library code. One may think that the solution for the uncaught exceptions may be to define a general handler, 
which is responsible for handling any exception that is not
adequately handled inside the applications. Although this 
solution may prevent  the system of abruptly crashing,
 such general handler will not have enough
contextual information to adequately handle the exception, 
a possible handler task is: to present a message to the user
 and restart the application. However, such handler cannot replace a carefully designed exception 
handling policy~\cite{Robil00}, which can hardly be designed in the absence of 
third-party documentation on the exceptions that
may the thrown by it. On the other hand, documenting runtime exceptions is a tedious and error prone task, to help developers
mitigate this problem tools should be developed to automate the documentation of runtime exceptions
scraping from library code, few solutions in this directions have been proposed so far~\cite{van2005combining}.

@@

%\noindent
\emph{Internal Validity.} We used a heuristics-based parser to mine
exceptions from issues.  Our parsing strategy was conservative by default; for
example, we only considered exception names using a fully qualified class name
as valid exception identifiers, while, in many cases, developers use the
exception name in issue description. Conservative parsing may minimize false
positives, which was our initial target, but also tends to increase false
negatives, which means that some cases may have not been identified as
exceptions or stack traces. Our limited manual inspection did not reveal such
cases. Moreover, in this study we manually mapped the concerns related to exceptions.
 To ensure the quality of the analysis, we calculated the interrater agreement after three independent 
developers classified a randomly selected sample (of 25 exception 
types from the total of 100); the interater agreement was high (96\%). 
Another threat relates to the fact that parts of our analysis 
are based on the availability of stack traces on issues reported on Github and Googlecode projects. 
In using these datasets, we make an underlying assumption: the stack traces reported on issues are 
representative of valid crash information of the applications. 
One way to mitigate such threat would be to access to the full 
set of crash data per application. Although some services exist 
to collect crash data from mobile applications~\cite{BugSe14,BugSn14,Googl14,Acra14},
they do not provide open access to the crash reports of their client applications.
In our study, we mitigated this threat by manually inspecting
the source code associated to a subset of the reported exception stack traces.
Such subset comprises the stack traces related to the main findings 
of the study (e.g., ``undocumented runtime and checked exceptions",
and cross-type wrappings").
%\noindent

\emph{External Validity.} Our work uses GHTorrent dataset; although 
comprehensive and extensive is not an exact replica of Github. 
However, the result of this study does not depent on the analysis of
a complete Github dataset. Instead, the goal of our study was to 
pinpoint \emph{bug hazards} on the exception-related code based on 
exception stack trace mining of a subset of projects.
We limited our analysis to a subset of existing open-source Android projects.
We are aware that the exception stack traces reported 
for commercial apps can be different from the ones found in this study, and that
this subset is a small percentage of existing apps.
Such threats are similar to the ones imposed to other empirical studies 
which also used free or open-source Android apps~\cite{Linar13,McDon13,Ruiz12}.
Moreover, several exception stack traces that support the findings of this study
refered to exceptions coming from methods defined on Android Application Framework
and third-party libraries.  Additionaly,  the \emph{bug hazards} observed in this study are due to
characteristics of Java exception model, which can impose challenges 
the robustness of not only to Android apps but also to other systems
 based on the same exception model.

@@

\textit{Empirical Studies on Exception Handling Defects.} 
Cabral and Marques~\cite{cabral2007exception} analyzed the
source code of 32 open-source systems, both for Java and .NET. They
observed that the actions inside handlers were very simple (e.g., logging and present a
message to the user). Coelho et al.~\cite{coelho2008assessing} performed an 
empirical study considering the fault-proneness of aspect-oriented implementations 
for handling exceptions. Two releases of both Java and AspectJ implementations were 
assessed as part of that study. Based on the use of an exception
flow analysis tool, the study revealed that the AOP  refactoring increased the 
number of uncaught exceptions, degrading the robustness of the AO version of every analyzed system.
The main limitation of approaches based static analysis based approaches are the number of false
positives they can generate, and the problems the faced when dealing with reflection libraries 
and dynamic class loading. Pingyu and Elbaum~\cite{Zhang12} were the first to perform
an empirical investigation of issues, related to exception-related bugs, on Android projects.  
They perform a small scale study on which they manually inspected the issues of 
5 Android applications. They observed that 29\% had to do with poor
exceptional handling code, this empirical study was used to motivate the development of a tool
aiming at amplifying existing tests to validate exception 
handling code associated with external resources. This work inspired ours,
 which automaticaly mined the exception stack traces embedded on issues 
reported on 639 open source Android projects. The goal of our study was
to identify common \emph{bug hazards} on the exception related code that can lead to 
failures such as uncaught exceptions.
